Constant-round Blind Classical Verification of Quantum Sampling

### 2022-02-28 qpip0.tex
Start preparing conference ver.

\hannote{maybe some explanation about $P_{acc,i}$ and $P_{acc,j}$ commute. maybe just stress that $P_{acc}$'s are in standard basis.stress on the dilation dequantization?} We denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as $P_{acc,-i,z}$.
Note that $P_{acc,-i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$. $P_{acc,-i,z}$ is a projector because it only involves the standard basis measurements to get $a$ and classical post-processing of the verifiers. Also note that  $P_{acc,-i,z} P_{acc,-i,z'}=0$ for all $z\neq z'$, and $\sum_z P_{acc,-i,z} =\Pi_{j \neq i} P_{acc,j}\leq Id$.

>>>>

We denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as $P_{acc,-i,z}$.
Note that $P_{acc,-i,z}$ also depends on $\vec{pk}, \vec{y}$, and $(sk_i, h_i)$ since it includes the measurement the prover did before sending $\vec{a}$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$. $P_{acc,-i,z}$ is a projector because it only involves the standard basis measurements to get $a$ and classical post-processing of the verifiers. Also note that  $P_{acc,-i,z} P_{acc,-i,z'}=0$ for all $z\neq z'$, and $\sum_z P_{acc,-i,z} =\Pi_{j \neq i} P_{acc,j}\leq Id$.
